---
title: "Assumptions"
author: "Ali Thursland and Mary Helen Wood"
date: "12/10/2018"
output: pdf_document
---

# == Setup ==

```{r setup, warning=FALSE, echo=FALSE, message=FALSE}
#Setup
library("dplyr")
library("ggplot2")
library("broom")
library("knitr")
library("cowplot")
library("readr")
library("dslabs")
library("varhandle")
library("olsrr")
library("car")
```

# == Read in Data == 

```{r data, warning=FALSE, message=FALSE, echo=FALSE}
airbnb <- read_csv("https://raw.githubusercontent.com/athursland/STA-210/master/finalairbnb.csv")
```

## Separate training and testing
```{r separate}
#80% of the sample size
smp_size <- floor(0.80 * nrow(airbnb))

#set the seed to make your partition reproducible
set.seed(123456)
train_ind <- sample(seq_len(nrow(airbnb)), size = smp_size)

train.airbnb <- airbnb[train_ind, ]
test.airbnb <- airbnb[-train_ind, ]
```

# == Final Model == 

```{r final-model}
stepwise.interactions.model <- lm(logprice ~ cleaning_fee * accommodates + availability_30 * minimum_nights
+ host_is_superhost
+ room_type
+ accommodates
+ cleaning_fee
+ minimum_nights
+ availability_30
+ log.reviews_per_month
+ cancellation_policy, data=train.airbnb)

kable(tidy(stepwise.interactions.model), format="markdown", digits = 4)
kable(glance(stepwise.interactions.model))
```
```

# == Assumptions == 

There are 5 assumptions for multiple linear regression:
1. Linearity
2. Constant variance 
3. Normality
4. Independence 

Additionally, we must avoid outliers/multicollinearity in our final model. 

```{r pairs-plots}
pairs(logprice ~ accommodates + bathrooms, data = train.airbnb)
```

```{r resids 2}
train.airbnb <- train.airbnb %>% mutate(stand.resid = rstandard(stepwise.interactions.model),
                                        pred = predict(stepwise.interactions.model))

```

```{r stand-resids-qq}
ggplot(data = train.airbnb, aes(x=stand.resid)) + geom_histogram()
qqnorm(train.airbnb$stand.resid)
```

```{r resids-explanatory}
p1 <- ggplot(data = train.airbnb, aes(x=pred, y=stand.resid)) + geom_point() + 
  labs(x="Predicted", y="Residual", title="Residuals vs Predicted",
subtitle=("backwards.interactions.model"))+
theme(plot.title = element_text(hjust = 0.5,size=14),
plot.subtitle=element_text(hjust=0.5,size=10))


p2 <- ggplot(data = train.airbnb, aes(x=accommodates, y=stand.resid)) + geom_point() + 
  labs(x="Number of Guests", y="Residual", title="Residuals vs Accommodates",
subtitle=("backwards.interactions.model"))+
theme(plot.title = element_text(hjust = 0.5,size=14),
plot.subtitle=element_text(hjust=0.5,size=10))

p3 <- ggplot(data = train.airbnb, aes(x= cleaning_fee, y=stand.resid)) + geom_point() + 
  labs(x="Fee ($)", y="Residual", title="Residuals vs Cleaning Fee",
subtitle=("Backwards.interactions.model"))+
theme(plot.title = element_text(hjust = 0.5,size=14),
plot.subtitle=element_text(hjust=0.5,size=10))

p4 <-ggplot(data = train.airbnb, aes(x=minimum_nights, y=stand.resid)) + geom_point() + 
  labs(x="Minimum Nights", y="Residual", title="Residuals vs Minimum_nights",
subtitle=("Backwards.interactions.model"))+
theme(plot.title = element_text(hjust = 0.5,size=14),
plot.subtitle=element_text(hjust=0.5,size=10))

p5 <- ggplot(data = train.airbnb, aes(x=availability_30, y=stand.resid)) + geom_point() + 
  labs(x="Number of Available Nights in the next month", y="Residual", title="Residuals vs Availability",
subtitle=("backwards.interactions.model"))+
theme(plot.title = element_text(hjust = 0.5,size=14),
plot.subtitle=element_text(hjust=0.5,size=10))

p6 <- ggplot(data = train.airbnb, aes(x=log.reviews_per_month, y=stand.resid)) + geom_point() + 
  labs(x="Reviews per month", y="Residual", title="Residuals vs Log Reviews per month",
subtitle=("backwards.interactions.model"))+
theme(plot.title = element_text(hjust = 0.5,size=14),
plot.subtitle=element_text(hjust=0.5,size=10))
```

```{r plot-residuals}
plot_grid(p1,p2,p3,p4)
plot_grid(p5,p6)
```

```{r outliers}
train.airbnb <- train.airbnb %>%
  mutate(leverage = hatvalues(stepwise.interactions.model), 
         cooks = cooks.distance(stepwise.interactions.model),
         obs.num = row_number())

ggplot(data=train.airbnb, aes(x=obs.num,y=leverage)) + 
  geom_point(alpha=0.5) + 
  geom_hline(yintercept=36/1520,color="red")+
  labs(x="Observation Number",y="Leverage",title="Leverage")

ggplot(data=train.airbnb, aes(x=obs.num,y=cooks)) + 
  geom_point() + 
  geom_hline(yintercept=1,color="red")+
  labs(x="Observation Number",y="Cook's Distance",title="Cook's Distance")

tidy(vif(stepwise.interactions.model))
```
